\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-07-12 manuscript.Rnw
Remove unnecessary abbreviations within abstract

%% - \Abstract{} almost as usual
\Abstract{
Health economic models simulate the costs and effects of health technologies for use in health technology assessment (HTA) to inform efficient use of scarce resources. Models have historically been developed using spreadsheet software (e.g., Microsoft \proglang{Excel}) and while use of \proglang{R} is growing, general purpose modeling software is still limited. \pkg{hesim} is an \proglang{R} package that helps fill this gap by facilitating parameterization, simulation, and analysis of economic models in an integrated manner. Supported model types include cohort discrete time state transition models (cDTSTMs), individual continuous time state transition models (iCTSTMs), and partitioned survival models (PSMs), encompassing Markov (time-homogeneous and time-inhomogeneous) and semi-Markov processes. A modular design based on \pkg{R6} and \code{S3} classes allows users to combine separate submodels for disease progression, costs, and utility in a flexible way. Probabilistic sensitivity analysis (PSA) is used to propagate uncertainty in model parameters to model outputs. Simulation code is written in \proglang{C++} so complex simulations such as those combining PSA and individual simulation can be run much more quickly than previously possible. Decision analysis within a cost-effectiveness framework is performed using simulated costs and quality-adjusted life years (QALYs) from a PSA.
}

>>>>

%% - \Abstract{} almost as usual
\Abstract{
Health economic models simulate the costs and effects of health technologies for use in health technology assessment to inform efficient use of scarce resources. Models have historically been developed using spreadsheet software (e.g., Microsoft \proglang{Excel}) and while use of \proglang{R} is growing, general purpose modeling software is still limited. \pkg{hesim} is an \proglang{R} package that helps fill this gap by facilitating parameterization, simulation, and analysis of economic models in an integrated manner. Supported model types include cohort discrete time state transition models, individual continuous time state transition models, and partitioned survival models, encompassing Markov (time-homogeneous and time-inhomogeneous) and semi-Markov processes. A modular design based on \pkg{R6} and \code{S3} classes allows users to combine separate submodels for disease progression, costs, and utility in a flexible way. Probabilistic sensitivity analysis (PSA) is used to propagate uncertainty in model parameters to model outputs. Simulation code is written in \proglang{C++} so complex simulations such as those combining PSA and individual simulation can be run much more quickly than previously possible. Decision analysis within a cost-effectiveness framework is performed using simulated costs and quality-adjusted life years from a PSA.
}
